\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Hyperlink settings
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

% Section settings
\titleformat{\section}{\large\bfseries}{}{}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{}{}
\titlespacing{\section}{0pt}{12pt}{6pt}
\titlespacing{\subsection}{0pt}{8pt}{4pt}

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}

% Name
{\LARGE\bfseries Felipe Azevedo Ribeiro}

\vspace{0.3cm}

% Contact
\href{mailto:feliper.dev@gmail.com}{feliper.dev@gmail.com} | 
\href{https://github.com/feliperfdev}{github.com/feliperfdev} | 
\href{https://www.linkedin.com/in/feliperdev}{linkedin.com/in/feliperdev} | 
\href{https://www.feliperdev.link}{feliperdev.link} | 
\href{tel:+5571996446771}{+55 (71) 996446771}

\section*{Summary}

Mid-level Mobile Developer specialized in Flutter with expertise in native Android and iOS development. Focused on continuous delivery with clean, testable, maintainable code, technical collaboration, and code reviews. Ensures UI/UX excellence with pixel-perfect design fidelity and performance optimization. Committed to agility, proactivity, and continuous improvement.

\section*{Education}

\textbf{Computer Engineering} — SENAI Cimatec University — Salvador/BA, Brazil — 2020–2025

\section*{Skills}

\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item \textbf{Mobile:} Flutter, Dart, BLoC, Provider, Riverpod, MobX, Drift ORM, Secure Storage, Geolocation, Flutter Web, Android/Kotlin Interoperability, Push Notifications (FCM), Offline-first, Caching
    \item \textbf{Backend:} Node.js, TypeScript, Express.js, NestJS
    \item \textbf{Cloud/DevOps:} AWS Lambda, API Gateway, DynamoDB, Cognito, Docker, CI/CD, GitHub Actions, Fastlane
    \item \textbf{Data:} PostgreSQL, Supabase, Firebase, MySQL, SQLite
    \item \textbf{Architecture/Quality:} Clean Architecture, Hexagonal Architecture, MVVM, DDD, TDD, REST APIs, gRPC, Protocol Buffers, Unit/Widget Tests, Sentry, Mixpanel
    \item \textbf{Design:} Figma, Rive, Lottie
    \item \textbf{Languages:} Portuguese (Native), English (B2)
\end{itemize}

\section*{Professional Experience}

\subsection*{Software Engineer | F.R Dev | 2024–2025}

\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Designed and developed Micro-SaaS web and mobile applications with Flutter and serverless backend (AWS/Supabase) applying DDD, hexagonal architecture, and offline-first strategies with synchronization, sync-queue, and caching.
    \item Built REST APIs with Node.js and Express.js prioritizing security and scalability.
    \item Implemented CI/CD, unit/widget tests, and Docker, improving reliability and release velocity.
    \item Ensured pixel-perfect design fidelity and optimized performance by monitoring response time and memory consumption.
\end{itemize}

\subsection*{Mobile Developer | Petize | 2023–2025}

\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Applied Hexagonal Architecture with TDD, achieving high coverage in core modules and reducing production bugs.
    \item Implemented BLoC pattern for state management, ensuring separation of concerns between UI and business logic; Optimized Lottie animations, maintaining consistent 60fps.
    \item Automated release pipeline (Fastlane + CI/CD) with automated testing.
    \item Led REST API integrations and push notifications (Firebase Cloud Messaging).
\end{itemize}

\subsection*{Mobile Developer | Ommed | 2021}

\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Implemented Clean Architecture + TDD in critical features.
    \item Established microservice communication via gRPC/Protocol Buffers.
    \item Managed complex state with MobX and reactive asynchronous flows.
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Aibum — Image generation for coloring. Flutter Web; APIs with Supabase and Express.js
    \item KeepLinked — Link organization with folders/tags/privacy. Flutter; APIs with Supabase/Express.js
    \item Wander Level — Offline-first mobile app with sync-queue. Flutter; Drift ORM; Supabase
    \item FinanceTracker — Mobile app for personal finance. Flutter; AWS backend (DynamoDB, Lambda, API Gateway, Cognito)
\end{itemize}

\end{document}